Processing genome scale tabular data with wormtable

### 2013-08-21 docs/paper/paper.tex
modified up to discussion

This difference is well illustrated by immediately repeating 
the same experiment, so that all the relevant pages are 
in cache. In this case, the elapsed time was 56 seconds for Tabix and around 
2 seconds for wormtable. Thus, compression is a double-edged sword: 
it does lead to much smaller files, which reduces the number of random seeks 
required.  On the other hand, however, decompression is expensive and must 
be repeated each time a block is accessed unless some sophisticated
caching mechanism is devised.

>>>>

This difference is well illustrated by immediately repeating 
the same experiment, so that all the relevant pages are 
in cache. In this case, the elapsed time was 56 seconds for Tabix and around 
2 seconds for wormtable. Thus, the use of compression is a trade-off: 
it reduces file size, which reduces the number of random seeks 
required but decompression is expensive and must 
be repeated each time a block is accessed.
